Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-08 thesis/paper.tex
notes to data analysis

%Reduce human error
The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results. If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.

%Interviews
After the initial source code inspection and preliminary analysis had been performed, interviews were conducted. The main purpose of the interviews was to validate our findings during the code inspection with the designers of the APIs. Ideally, the interviews would provide additional insight into decisions and motives behind changes that were not evident from the code inspection. The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API and how their decisions, needs and requirements have affected the development of the API.

\subsection{Data Analysis} \label{data_analysis}
%Intro and summary
The data analysis was conducted in two major phases \cite{andersson2007spiral}. During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study. It was during this phase that the analysis of the API code and documentation was carried out. The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase. Both phases were performed iteratively, together with the data collection. This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.

%Initial state with the data - It's in tables as raw changes here
Once the preliminary groups of changes were identified, we had to identify what was different between the two versions.

>>>>

%Reduce human error
%We could consider joining this sentence with the previous paragraph. WWW
The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results. If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.

%Interviews 
%I changed stuff in here WWW
After the initial source code inspection and preliminary analysis had been performed, an interview was conducted. The main purpose of the interview was to validate our findings during the code inspection with the API architect. The interview also served the purpose of providing additional insight into what drives the API evolution, by complementing what was found from the code inspection. The final reason for interviewing the API architects was to gather information about the API users and how their decisions, needs and requirements have affected the development of the API.

\subsection{Data Analysis} \label{data_analysis}

1. Grounded theory

2. RQ1

3. RQ2

4. Interviews

5. RQ1.1

%Intro and summary
The data analysis was conducted in two major phases \cite{andersson2007spiral}. During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study. It was during this phase that the analysis of the API code and documentation was carried out. The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase. Both phases were performed iteratively, together with the data collection. This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.

%Initial state with the data - It's in tables as raw changes here
Once the preliminary groups of changes were identified, we had to identify what was different between the two versions. %%Preliminary groups=?, "had to", what was different"=not descriptive enough
